---
title: "Lab 11"
author: "Reed Magleby"
date: "November 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function that generates numbers from binomial(n, p) distribution using runif() function. Hint:
binomial(n, p) random variable can be defined as a sum of n independent Bernoulli(p) random variables.

```{r}
binomial <- function(n, size, p) {
  binom_vect2 <- replicate((n = n), {
    binomvect <- runif(n = size)
    logicalvector <- ifelse(binomvect >= 0.5, 1, 0)
    sum(logicalvector)
  })
  return(binom_vect2)
}

rbinom(10,100,0.5)
binomial(10,100,0.5)
```


2. Compare performance of your function with rbinom() using microbenchmark() function.

```{r}

library(microbenchmark)
microbenchmark(binomial(1000, 1000, 0.5), rbinom(1000, 1000, 0.5))
```


3. Suppose we want to simulate data from a linear regression model:
Yi = ??0 + ??1 × Xi + i i = 1, ..., N
where  ??? N(0, 3) and X is a covariate that ranges between 20 and 40. Let ??0 = 15 and ??1 = 0.4 are known
coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model
and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function
for reproducibility.

```{r}
library(tidyverse)
set.seed(123)

x <- sample(20:40, 50, replace = TRUE)
error <- rnorm(50, 0, 3)
model <- 15 + (0.4 * x) + error

model_frame <- data.frame(lm(model ~ x)$fitted, lm(model ~ x)$residuals, col.names = c("x", "y"))
colnames(model_frame) <- c("x", "y")

ggplot(data = model_frame) +
  geom_point(aes(x = x, y = y)) +
  labs(x = "Fitted values", y = "residuals")
```


4. Box-Muller algorithm: generate U1 and U2 two independent uniform(0, 1) random variables and set:
R =
p
???2 log(U1) and ?? = 2??U2
then
X = R cos(??) and Y = R sin(??)
are two independent normal variables. Write a function that generates normal variates using Box-Muller
algorithm. Compare simulated data from your function with simulated data from rnorm() function
using ggplot() (histogram?).

```{r}
boxmuller <- function(n) {
  u1 <- runif(n, 0, 1)
  u2 <- runif(n, 0, 1)
  r <- sqrt(-2 * log(u1))
  theta <- 2 * pi * u2

  x <- r * cos(theta)
  y <- r * sin(theta)
}

model <- data.frame(boxmuller(1000))
normal <- data.frame(rnorm(1000))

ggplot() +
  geom_freqpoly(data = model, aes(model$boxmuller.1000., stat(density), color = "Box Muller Model")) +
  geom_freqpoly(data = normal, aes(normal$rnorm.1000., stat(density), color = "Normal Model")) +
  labs(x = NULL)
```


